Interpolation of Sparse High-Dimensional Data\thanks {This work was supported by the National Science Foundation Grant CNS-1565314.}

### 2020-08-13 [2019-02]_NUMA_(interpolant_error_bound)/tchlux-NA-interpolation/Versions/2-response.tex
Finished NUMA paper and submitted. Might need to do one more round with editors.

Addressed by item \ref{review:item1}.

@@

All of these have been addressed in each individual subsection and in part by item \ref{review:item2} above. Regarding the shape of $W_k$ in Modified Shepard and LSHEP, the weight equation was rewritten to provoke a more clear understanding in accompaniment with the visual.

@@

The phrasing has been changed (page \hyperlink{page.10}{10}). This is a reference the process of converting source data into predictions and then measuring the error.

@@

This is a misunderstanding. The paper reads ``\ldots polynomials of \color{red}degree \color{black} $n+1$.'' and the degree of a polynomial is one less than the order. So order $n$ polynomials are used here.

@@

This suggestion is appreciated. Such specific outcomes are not obviously related to the error bound theorem, which is the central component of this paper. For this reason, we would like to abstain from including information that might distract readers from the main purposes of the text.

>>>>

Addressed by item \ref{review:item1}. However, sparse grids are not included in the comparison because they do not scale beyond tens of dimensions and are primarily used for applications where data points can be chosen (although as a reviewer mentioned, they can be applied to scattered data problems).

@@

All of these have been addressed in each individual subsection and in part by item \ref{review:item2} above. Regarding the shape of $W_k$ in Modified Shepard and LSHEP, the weight equation was rewritten to provide a more clear understanding in accompaniment with the visual.

@@

The phrasing has been changed (page \hyperlink{page.10}{10}). This is a reference to the process of converting source data into predictions and then measuring the error.

@@

This is a misunderstanding. The paper reads ``\ldots polynomials of \color{red}degree \color{black} $n+1$.'' For these Fekete points we chose a polynomial basis of size $2N$ and have fixed $d$, but there is not necessarily a value of $n$ for which ${n + d \choose n} = 2N$, so we must augment the ${n+d \choose n}$ basis polynomials of degree $n$ with a few higher degree ones to get exactly $2N$.

@@

Done on page \hyperlink{page.29}{29} and referenced at the beginning of the empirical results section on page \hyperlink{page.17}{17}
